---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# crtb

<!-- badges: start -->
<!-- badges: end -->

The goal of crtb is to complementary resampling of tags in blocks.

## Installation

You can install the development version of crtb from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mightymetrika/crtb")
```

## Complementary Resampling of Tags in Blocks

With multiple groups and pooled resampling, crtb is implemented as follows:

- Tagging: assign each observation a unique integer.
- Resample the tags (with replacement, without replacement, or custom). This is the original resample.
- Quit if resample has more repeated tags than allowed by tie threshold.
- Create blocks (note: block size is 1/2 the length of initial tags)
 - Get first block of unique tags
 - Get unique remaining tags as the block stem for the second block
  - If the block stem forms the full block size then the process is complete
  - If the block stem is shorter then the block size, fill out the block by taking the set difference between a resample without replacement of all tags and the block stem.
 - Repeat the previous step until all tags in the original resample are included in a block.
- Get the complement of the tags in each block
- In each complement, only keep the number of elements from the corresponding block's block stem. The retained collection of tags corresponds to the complementary resample.
- Map the tags back onto the original observations
- Return the datasets corresponding to the original resample and to the complementary resample.

```{r example}
library(crtb)
## basic example code
```

