---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Complementary Resampling of Tags in Blocks (CRTB)

<!-- badges: start -->
<!-- badges: end -->

The crtb resampling method is inspired by complementary pairs subsampling (Shah & Samworth, 2013). The method creates pairs of resampled datasets with complementary properties.

## Installation

You can install the development version of crtb from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mightymetrika/crtb")
```

## Implementation Details

When working with multiple groups and pooled resampling, CRTB follows these steps:

1. **Tag Assignment**
  - Each observation receives a unique integer tag
  - For multiple groups, tagging can be done row-wise or column-wise
 
2. **Initial Resampling**
  - Tags are resampled using one of three methods
    - With replacement (default)
    - Without replacement
    - Custom resampling function
  - This creates the "original resample"
  - Process halts if the proportion of resamples falls below the tie threshold

3. **Block Creation**
  - Block length is set to half the length of initial tags
  - First block:
    - Form initial block stem from unique tags in original sample
    - If block stem is undersized:
      1. Take the set difference between all tags and block stem
      2. Sample without replacement to fill block to target size
  - Subsequent blocks:
    - Form new block stem from unique remaining tags
    - If block stem is undersized:
      1. Take the set difference between all tags and block stem
      2. Sample without replacement to fill block to target size
  - Continue until all tags from original sample are assigned to blocks
 
4. **Complementary Sampling**
  - For each block:
    - Find complement (all tags not in block)
    - Sample from complement to match block stem size
  - Combined complementary samples form the "complementary resample"
 
5. **Output Generation**
  - Map tags back to original observations
  - Return two datasets:
    - Original resample
    - Complementary resample

```{r example}
library(crtb)

# Create sample data
data <- data.frame(
  group1 = stats::rnorm(10),
  group2 = stats::rnorm(10)
)

# Basic usage with default settings
result <- crtb(data)

# Access results
result$ordat
result$crdat
```


Shah, R. D., & Samworth, R. J. (2013). Variable Selection with Error Control: Another Look at Stability Selection. Journal of the Royal Statistical Society: Series B, 75(1), 55-80.
